Language-Based Security for Low-Level MPC

### 2024-05-18 ppdp24/model.tex
checkpoint

Another important distinction of the malicious setting is that it
typically incorporates \emph{abort}. Honest parties implement
strategies to detect rule-breaking-- aka \emph{cheating}-- by
using, e.g., message authentication codes with semi-homomorphic
properties as in BDOZ and SPDZ \cite{XXX}. If cheating is
detected, the protocol is aborted. To model this, we extend
$\minifed$ with an \ttt{assert} command and extend the
range of memories with $\bot$. Note that the adversary is
free to ignore their own assertions.
\begin{definition}
  We add assertions of the form $\elab{\assert{\phi(\be)}}{\cid}$ to the command
  syntax of $\minifed$, where $\phi$ is a decidable predicate on
  $\mathbb{F}_p$ and with operational semantics given in Figure
  \ref{fig-adversary}. We also extend the range of memories $\store$
  to $\mathbb{F}_p \cup \{ \bot \}$.
\end{definition}

>>>>

A key technical distinction of the malicious setting is that it
typically incorporates ``abort''. Honest parties implement strategies
to detect rule-breaking-- aka \emph{cheating}-- by using, e.g.,
message authentication codes with semi-homomorphic properties as in
BDOZ/SPDZ \cite{10.1007/978-3-030-68869-1_3}. If cheating is detected,
the protocol is aborted. To model this, we extend $\minifed$ with an
\ttt{assert} command and extend the range of memories with
$\bot$. Note that the adversary is free to ignore their own
assertions.
\begin{definition}
  We add assertions of the form $\elab{\assert{\phi(\be)}}{\cid}$ to the command
  syntax of $\minifed$, where $\phi$ is a decidable predicate on
  $\mathbb{F}_p$ and with operational semantics given in Figure
  \ref{fig-adversary}. We also extend the range of memories $\store$
  to $\mathbb{F}_p \cup \{ \bot \}$.
\end{definition}
